\documentclass{cidr}

\title{CIDR 2003 Submission Style Guide (Latex document)}

\author{Author Name}

\institution{Organization\\
Address\\
Town\\
Country\\
Email@small.medium.large}


\begin{document}
\maketitle

\begin{abstract}
The abstract for your paper for the 2003 CIDR Conference.
\end{abstract}


\section{Guidelines for submission}

These guidelines must be read in conjunction with the information for
authors.

\section{Format, style and content}

\subsection{Page size}

All papers must be on 8 1/2" x 11" white bond paper (US letter format). 
The format of the submission should follow this sample for layout, type
sizes, and other details.  However, there are variations among the many
typesetting and word-processing packages in use.  If you cannot
replicate these specifications exactly, you may develop useable styles
by approximating these guidelines where necessary.


\subsection{First page}

The top margin should be 1"; the title should be centered, with initial
capitals, in boldface. Leave a gap of 7/16" after the title.

If there is only one author, the name should be centered, with initial
capitals, in Roman font. If there are two authors, the first author
should be flush left, and the second author flush right.  If there are
more than two authors, the first author should flush left, the second
author should be centered, the third author should be flush right, and
so on.  Affiliations should be centered under each author name. Leave a
gap of 7/16" to the first line of text.


\subsection{Main text}

Manuscripts must be printed two columns to a page.  The dimensions of
the columns are 3-1/4" wide, 7/8" margins in the right and left sides,
and 1/4" gap between the two columns.  The bottom margin in all cases is
1 1/8". Start the text on all pages except the first page at 3/4" below
the top of the page.

For the body of the text, use 10-point type in a clear, readable font
(Times-Roman or equivalent), with 1-point leading (i.e., 10 on 11).

\subsection{Abstract}

Begin the first paragraph (page one, column one) with the abstract,
indented 1/4" on both sides.

\subsection{Headings}

Headings should be in 12-point type, with 1 line of space above, and
one-half line of space below.

\subsection{Tables and figures}

Table and figures should be centered in one-column, or centered at top
of page if the figure is larger than a column in width.


\subsection{Page numbering, headers and footers}

Do not include headers, footers or page numbers in your final
submission. These will be added when the publication is assembled.
However, for the version submitted for refereeing only you may include
page numbers.

\subsection{Copyright Notice}

Include a copyright notice at the bottom of the first column, containing
the text used here. In this document, it has been placed in a frame to
fix its position. The copyright notice is not necessary for the version
submitted for refereeing.

\section{Example document}

This document is an example of the recommended format and uses the {\em
vldb.cls} style file.  Even if you use this document as the basis for
formatting your submission, you must still check that, when printed, the
hard copy meets the required format.


\bigskip

{\em Dimitris Papadias, dimitris@cs.ust.hk}

\end{document}
